Data_visualization

### 2018-08-30 Rmd/Data_visualization.Rmd

brol_seed_set <- read.csv("Data/BROL_seed_set.csv", sep=";")
brol_seed_set <- filter(brol_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("BROL", 10)
Treatment <- rep("BROL 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brol_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("BROL", 10)
Treatment <- rep("BROL 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brol_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(brol_seed_set)[1] <- "Species"
colnames(brol_seed_set)[2] <- "Treatment"
colnames(brol_seed_set)[3] <- "Treatment.number"
colnames(brol_seed_set)[4] <- "Seed.production"
brol_seed_set <- rbind(brol_seed_set, brol_50, brol_100)
brol_seed_set$Treatment<- as.character(brol_seed_set$Treatment)
brol_seed_set <- brol_seed_set[order(brol_seed_set$Treatment),]

library(stringr)
brol_seed_set_div <- str_split_fixed(as.character(brol_seed_set$Treatment), " ", 2)
brol_seed_set_div <- data.frame(brol_seed_set_div, stringsAsFactors = F)
colnames(brol_seed_set_div)=c("non_focal","percentage")
brol_seed_set_bind <- cbind(brol_seed_set,brol_seed_set_div)
brol_seed_set_bind <- filter(brol_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(brol_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

brol_seed_set_cross <- filter(brol_seed_set_bind, non_focal %in% c("Cross"))
brol_seed_set_self <- filter(brol_seed_set_bind, non_focal %in% c("Self"))
brol_seed_set_control <- filter(brol_seed_set_bind, non_focal %in% c("Control"))
brol_seed_set_flower <- filter(brol_seed_set_bind, non_focal %in% c("FC"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Cross"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Self"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("Control"),]
brol_seed_set_bind=brol_seed_set_bind[brol_seed_set_bind$non_focal!=c("FC"),]

brol_seed_set_final<-rbind(brol_seed_set_bind,brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
                           brol_seed_set_flower)
#deleting extra columns used for data formating
brol_seed_set_final=brol_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
brol_seed_set_final[brol_seed_set_final$Treatment==c("BROL 50%"),4] <- NA

#changing non_focal species name
brol_seed_set_final$Treatment=as.character(brol_seed_set_final$Treatment)
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
brol_seed_set_final$Family[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
brol_seed_set_final$Treatment[brol_seed_set_final$Treatment=="FC"] <- "Flower control"

brol_seed_set_brassicaceae <- filter(brol_seed_set_final, Family %in% c("Brassicaceae"))
brol_seed_set_convolvulaceae <- filter(brol_seed_set_final, Family %in% c("Convolvulaceae"))
brol_seed_set_solanaceae <- filter(brol_seed_set_final, Family %in% c("Solanaceae"))
brol_seed_set_final$Family[is.na(brol_seed_set_final$Family)] <- "Solanum lycopersicum"

brol_seed_set_cross=brol_seed_set_cross[,-c(5,6)]
brol_seed_set_cross$Family <- "other"
brol_seed_set_self=brol_seed_set_self[,-c(5,6)]
brol_seed_set_self$Family <- "other"
brol_seed_set_control=brol_seed_set_control[,-c(5,6)]
brol_seed_set_control$Family <- "other"
brol_seed_set_flower=brol_seed_set_flower[,-c(5,6)]
brol_seed_set_flower$Family <- "other"

brol_seed_set_final=rbind(brol_seed_set_brassicaceae, brol_seed_set_convolvulaceae, 
                          brol_seed_set_solanaceae, brol_seed_set_cross, brol_seed_set_self, brol_seed_set_control,
                          brol_seed_set_flower)
#Different colour per family
a <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

brra_seed_set <- read.csv("Data/BRRA_seed_set.csv", sep=";")
brra_seed_set <- filter(brra_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("BRRA", 10)
Treatment <- rep("BRRA 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brra_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("BRRA", 10)
Treatment <- rep("BRRA 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
brra_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(brra_seed_set)[1] <- "Species"
colnames(brra_seed_set)[2] <- "Treatment"
colnames(brra_seed_set)[3] <- "Treatment.number"
colnames(brra_seed_set)[4] <- "Seed.production"
brra_seed_set <- rbind(brra_seed_set, brra_50, brra_100)
brra_seed_set$Treatment<- as.character(brra_seed_set$Treatment)
brra_seed_set <- brra_seed_set[order(brra_seed_set$Treatment),]

library(stringr)
brra_seed_set_div <- str_split_fixed(as.character(brra_seed_set$Treatment), " ", 2)
brra_seed_set_div <- data.frame(brra_seed_set_div, stringsAsFactors = F)
colnames(brra_seed_set_div)=c("non_focal","percentage")
brra_seed_set_bind <- cbind(brra_seed_set,brra_seed_set_div)
brra_seed_set_bind <- filter(brra_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(brra_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

brra_seed_set_cross <- filter(brra_seed_set_bind, non_focal %in% c("Cross"))
brra_seed_set_self <- filter(brra_seed_set_bind, non_focal %in% c("Self"))
brra_seed_set_control <- filter(brra_seed_set_bind, non_focal %in% c("Control"))
brra_seed_set_flower <- filter(brra_seed_set_bind, non_focal %in% c("Flower"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Cross"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Self"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Control"),]
brra_seed_set_bind=brra_seed_set_bind[brra_seed_set_bind$non_focal!=c("Flower"),]

brra_seed_set_final<-rbind(brra_seed_set_bind,brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
                           brra_seed_set_flower)
#deleting extra columns used for data formating
brra_seed_set_final=brra_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
brra_seed_set_final[brra_seed_set_final$Treatment==c("BRRA 50%"),4] <- NA

#changing non_focal species name
brra_seed_set_final$Treatment=as.character(brra_seed_set_final$Treatment)
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
brra_seed_set_final$Family[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
brra_seed_set_final$Treatment[brra_seed_set_final$Treatment=="FC"] <- "Flower control"

brra_seed_set_brassicaceae <- filter(brra_seed_set_final, Family %in% c("Brassicaceae"))
brra_seed_set_convolvulaceae <- filter(brra_seed_set_final, Family %in% c("Convolvulaceae"))
brra_seed_set_solanaceae <- filter(brra_seed_set_final, Family %in% c("Solanaceae"))
brra_seed_set_final$Family[is.na(brra_seed_set_final$Family)] <- "Solanum lycopersicum"

brra_seed_set_cross=brra_seed_set_cross[,-c(5,6)]
brra_seed_set_cross$Family <- "other"
brra_seed_set_self=brra_seed_set_self[,-c(5,6)]
brra_seed_set_self$Family <- "other"
brra_seed_set_control=brra_seed_set_control[,-c(5,6)]
brra_seed_set_control$Family <- "other"
brra_seed_set_flower=brra_seed_set_flower[,-c(5,6)]
brra_seed_set_flower$Family <- "other"

brra_seed_set_final=rbind(brra_seed_set_brassicaceae, brra_seed_set_convolvulaceae, 
                          brra_seed_set_solanaceae, brra_seed_set_cross, brra_seed_set_self, brra_seed_set_control,
                          brra_seed_set_flower)

#Different colour per family
b <- ggplot(caan_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ersa_seed_set <- read.csv("Data/ersa_seed_set.csv", sep=";")
ersa_seed_set <- filter(ersa_seed_set, Treatment!="RARA 100%" & Treatment!="RARA 50%"& Treatment!="COSA 50%"& Treatment!="COSA 100%" )

#adding the focal species, first 50%
Species <- rep("ERSA", 10)
Treatment <- rep("ERSA 50%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ersa_50 <- data.frame(Species,Treatment, Treatment.number, Seed.production)
#adding the focal species, 100%
Species <- rep("ERSA", 10)
Treatment <- rep("ERSA 100%", 10)
Treatment.number <- seq(1:10)
Seed.production <- rep(0, 10)
ersa_100<-  data.frame(Species,Treatment, Treatment.number, Seed.production)
#Order from lower to higher values the average, to plot it nicely
colnames(ersa_seed_set)[1] <- "Species"
colnames(ersa_seed_set)[2] <- "Treatment"
colnames(ersa_seed_set)[3] <- "Treatment.number"
colnames(ersa_seed_set)[4] <- "Seed.production"
ersa_seed_set <- rbind(ersa_seed_set, ersa_50, ersa_100)
ersa_seed_set$Treatment<- as.character(ersa_seed_set$Treatment)
ersa_seed_set <- ersa_seed_set[order(ersa_seed_set$Treatment),]

library(stringr)
ersa_seed_set_div <- str_split_fixed(as.character(ersa_seed_set$Treatment), " ", 2)
ersa_seed_set_div <- data.frame(ersa_seed_set_div, stringsAsFactors = F)
colnames(ersa_seed_set_div)=c("non_focal","percentage")
ersa_seed_set_bind <- cbind(ersa_seed_set,ersa_seed_set_div)
ersa_seed_set_bind <- filter(ersa_seed_set_bind, percentage!="100%")

#Because I want to give it specifically order I do it separately
#pein_seed_set_common <- filter(ersa_seed_set_bind, non_focal %in% c("CROSS", "SELF","CONTROL","FLOWER"))

ersa_seed_set_cross <- filter(ersa_seed_set_bind, non_focal %in% c("Cross"))
ersa_seed_set_self <- filter(ersa_seed_set_bind, non_focal %in% c("Self"))
ersa_seed_set_control <- filter(ersa_seed_set_bind, non_focal %in% c("Control"))
ersa_seed_set_flower <- filter(ersa_seed_set_bind, non_focal %in% c("Flower"))

# I HAVENT BEEN ABLE TO WORK OUT ALL AT THE SAME TIME SO i DO IOT SEPARATELY
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Cross"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Self"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Control"),]
ersa_seed_set_bind=ersa_seed_set_bind[ersa_seed_set_bind$non_focal!=c("Flower"),]

ersa_seed_set_final<-rbind(ersa_seed_set_bind,ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
                           ersa_seed_set_flower)
#deleting extra columns used for data formating
ersa_seed_set_final=ersa_seed_set_final[,-c(5,6)]
#adding NA'S to the focal species
ersa_seed_set_final[ersa_seed_set_final$Treatment==c("ERSA 50%"),4] <- NA

#changing non_focal species name
ersa_seed_set_final$Treatment=as.character(ersa_seed_set_final$Treatment)
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Brassicaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Solanaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Convolvulaceae"
ersa_seed_set_final$Family[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Convolvulaceae"

ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BROL 50%"] <- "Brassica oleracea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="BRRA 50%"] <- "Brassica rapa"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="CAAN 50%"] <- "Capsicum annuum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="ERSA 50%"] <- "Eruca vesicaria" #Eruca sativa seems to be a synonym
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPAQ 50%"] <- "Ipomoea aquatica"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="IPPU 50%"] <- "Ipomoea purpurea"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="PEIN 50%"] <- "Petunia integrifolia"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SIAL 50%"] <- "Sinapis alba"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOLY 50%"] <- "Solanum lycopersicum"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="SOME 50%"] <- "Solanum melongena"
ersa_seed_set_final$Treatment[ersa_seed_set_final$Treatment=="FC"] <- "Flower control"

ersa_seed_set_brassicaceae <- filter(ersa_seed_set_final, Family %in% c("Brassicaceae"))
ersa_seed_set_convolvulaceae <- filter(ersa_seed_set_final, Family %in% c("Convolvulaceae"))
ersa_seed_set_solanaceae <- filter(ersa_seed_set_final, Family %in% c("Solanaceae"))
ersa_seed_set_final$Family[is.na(ersa_seed_set_final$Family)] <- "Solanum lycopersicum"

ersa_seed_set_cross=ersa_seed_set_cross[,-c(5,6)]
ersa_seed_set_cross$Family <- "other"
ersa_seed_set_self=ersa_seed_set_self[,-c(5,6)]
ersa_seed_set_self$Family <- "other"
ersa_seed_set_control=ersa_seed_set_control[,-c(5,6)]
ersa_seed_set_control$Family <- "other"
ersa_seed_set_flower=ersa_seed_set_flower[,-c(5,6)]
ersa_seed_set_flower$Family <- "other"

ersa_seed_set_final=rbind(ersa_seed_set_brassicaceae, ersa_seed_set_convolvulaceae, 
                          ersa_seed_set_solanaceae, ersa_seed_set_cross, ersa_seed_set_self, ersa_seed_set_control,
                          ersa_seed_set_flower)

>>>>

brol_seed_set_final <- read.csv("Data/brol_seed_set_final.csv")
brol_seed_set_final=brol_seed_set_final[,-1]
#Different colour per family
a <- ggplot(brol_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica oleracea",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

brra_seed_set_final <- read.csv("Data/brra_seed_set_final.csv")
brra_seed_set_final=brra_seed_set_final[,-1]

#Different colour per family
b <- ggplot(brra_seed_set_final, aes(x = factor(Treatment, levels=unique(Treatment)), y = Seed.production)) +   geom_boxplot(outlier.shape = NA)+
  labs(title="Brassica rapa",x="", y = "Seeds")+aes(fill=Family)+theme(axis.text.x =element_blank())+
  theme(plot.title = element_text(hjust = 0.5)) +scale_fill_manual(values=cbPalette)+ geom_jitter(width = 0.3,shape=1,size=0.8, aes(colour=Family))+scale_color_manual(values = cbPalette) + stat_summary(fun.y=mean, geom="point", shape="*", size=5) +theme(legend.position="none")

@@

ersa_seed_set_final <- read.csv("Data/ersa_seed_set_final.csv")
ersa_seed_set_final=ersa_seed_set_final[,-1]
